% DFF template for Latex and A4 paper.
% 12pt Times New Roman on 1.5 line spacing and 2 cm margins.

% ----------------------------------------------------------------------

% Either format with 
%    pdflatex projectdescription.tex
% Or if you use dvips and ps2pdf, remember to specify A4 paper:
%    latex  projectdescription
%    dvips  -ta4 projectdescription -o projectdescription.ps
%    ps2pdf -sPAPERSIZE=a4 projectdescription.ps

% ----------------------------------------------------------------------

\documentclass[fleqn,12pt]{article}
%Do not change this geometry settings
\usepackage[a4paper,top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
%\usepackage{titlesec}
\hypersetup{
    colorlinks=true,
    linkcolor = black,
    citecolor =blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

% \usepackage{graphicx}         % For PDF figures
% \usepackage[dvips]{graphicx}  % For EPS figures, using dvips + ps2pdf

\begin{document}
% Empirically this seems to match MS Word's idea of 1.5 line spacing.
% DO NOT CHANGE
\setlength{\baselineskip}{1.44\baselineskip}


% ----------------------------------------------------------------------
% Enter the topic of the project and your names 

\begin{flushleft}
  {\large Gergo Gyori (gegy@itu.dk), BSc Data Science \\
  Katalin Literati-Dobos (klit@itu.dk), BSc Data Science \\
  Ludek Cizinsky (luci@itu.dk), BSc Data Science \\
  Lukas Rasocha (lukr@itu.dk), BSc Data Science \\}
 \end{flushleft}
 
\begin{center}
  {\Large Reflections on Data Science 2023}\\[5ex]
  {\Large Social Study: Herding effect on Reddit}\\[5ex]

 \end{center}
 

% ----------------------------------------------------------------------
% Delete the instruction 

%\parskip=3mm

%\noindent

\parindent=20pt 
\parskip=0mm

\section{Introduction}
Posts that achieve popularity on social media platforms, 
like Reddit, often outperform average posts significantly, 
which indicates a qualitative difference between popular posts 
and the rest. With this phenomenon an interesting question emerges:
is the success of a post attributable to its inherent quality,
or is it influenced by the herd effect? The social psychological 
behaviour that leads individuals to perceive an action as the 
appropriate course simply because it's what "everyone else" 
seems to be doing. This effect has already been documented in various studies such as \cite{muchnik} \cite{salganik}.
In this study we aim to investigate the herd effect on the Reddit platform, more
concretely, we want to find out to what extent does an initial upvote to a post
influence its future score?


\section{Experiment implementation}
Similar to Muchnik et al. \cite{muchnik}, to test the effect of a social
influence on upvoting reddit posts we conducted a randomised control trial.
For the continous period of seven days we collected and monitored recently published posts with no upvotes 
nor comments from the subreddit \textit{r/all}, and randomly assigned them 
to two categories: \textit{treatment} and \textit{control}.
The treatment group received an initial upvote, while the control group did not. 
The experiment was scheduled to run daily to ensure that the collected posts
had at least 24 hour period between the score loggings.

After the experimentation period ended, we aimed to test the following null hypothesis, with a significance
threshold $\alpha$ set to 0.05:
\textit{A treatment of a post does not influences its score (number of upvotes minus downvotes) in the future.}
Before the testing, some pre-processing steps were necessary. 
First, we removed the posts which were not continously monitored for a week and secondly,
to account for our initial upvote, we subtracted it from the posts' last day scores.
This resulted in a total number of $1578$ posts, i.e. $789$ treated posts and $789$ control posts. 
Finally, since we did not want to make assumptions about the underlying 
distribution of the data, we used non-parametric tests, namely Empirical bootstrap and Kolmogorov-Smirnov test, to
confirm or reject the studied null hypothesis.


\section{Results and discussion}

Discuss your findings in light of the theories and concepts covered in the course (e.g., causality, experimental designs,
extraneous variables, social influence, reproducibility, etc.)

Since we learned a bit too late about the vote fuzzing our experiment only recorded the overall score of the posts, while not looking at changing number of comments
which might have been a better indication (no comment count fuzzing).
\section{Conclusion}

% ----------------------------------------------------------------------
% References 

 \newpage 
%\section*{References}
\bibliographystyle{unsrt}
\bibliography{yourbib}

\end{document}